---
title: "Project1_Shengnan_Li"
author: "Shengnan LI"
date: "10/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(spData)
library(gganimate)
library(dplyr)
library(ggplot2)
library(rnaturalearth)
library(png)
library(gifski)

```

```{r}
col_names <- c(
  'SID',
  'SEASON',
  'NUMBER',
  'BASIN',
  'SUBBASIN',
  'NAME',
  'ISO_TIME',
  'NATURE',
  'LAT',
  'LON',
  'WMO_WIND',
  'WMO_PRES',
  'WMO_AGENCY',
  'TRACK_TYPE',
  'DIST2LAND',
  'LANDFALL'
)
```

```{r}
col_types <- c(
  'character',
  'integer',
  'integer',
  'character',
  'character',
  'character',
  'character',
  'character',
  'real',
  'real',
  'integer',
  'integer',
  'character',
  'character',
  'integer',
  'integer'
)
```

```{r}
url <- "ibtracs.NA.list.v04r00.csv"
Hurricanes <- read.csv(url, 
sep = ",",
colClasses = c(col_types, rep("NULL", 147)),
stringsAsFactors = FALSE,
skip = 77876, 
na.strings = "NA"
)
```


```{r}
colnames(Hurricanes) <- col_names
```

```{r}
Hurricanes$ISO_TIME = as.POSIXct(Hurricanes$ISO_TIME)
Hurricanes$MONTH <- lubridate::month(Hurricanes$ISO_TIME)
```

```{r}
str(Hurricanes, vec.len = 1)
```

C) Main Analysis 

C.1) Are hurricanes becoming more frequent?
In the analyzed period (from 1970 to 2019), are hurricanes becoming more frequent (year
over year generally speaking)?
Come up with both numeric and visual outputs to answer this research question, and include
a description/interpretation of such outputs.


```{r}                      
hurricanes_1970_2019_T <- filter(Hurricanes, SEASON %in% 1970:2019)
hurricanes_1970_2019 <- count(hurricanes_1970_2019_T,SID, SEASON)
unique_hurricanes_1970_2019 <- unique(select(hurricanes_1970_2019, SID, SEASON))

hurricanes_1970_2019_1 <- count(unique_hurricanes_1970_2019, SEASON)
hurricanes_1970_2019_1
ggplot(unique_hurricanes_1970_2019, aes(x = SEASON))+
  geom_bar() 
```

C.2) Are hurricanes getting stronger?
In the analyzed period (from 1970 to 2019), are hurricanes getting stronger (year over year
generally speaking)?
Come up with both numeric and visual outputs to answer this research question, and include
a description/interpretation of such outputs.

```{r}
year_max_wind <- 
  summarise(group_by(hurricanes_1970_2019_T, SEASON),
 max_wind = max(WMO_WIND,na.rm = TRUE)
)
ggplot(data = year_max_wind, aes(x = SEASON, y = max_wind)) +
  
  geom_line() +
  geom_smooth(method = 'lm')

```

C.3) 2019 Atlantic Hurricane Season
You will also have to investigate the following claims:
a) The 2019 atlantic hurricane season had 20 tropical cyclones, of which 18 were named
storms.

```{r}
# TRUE, the 2019 Atlantic hurricane season had 20 tropical cyclones, of which 18 were named.

Hurricanes_2019 <- filter(Hurricanes, SEASON == 2019)

distinct(Hurricanes_2019, SID)
distinct(Hurricanes_2019, WMO_WIND > 34)


Hurricanes_2019_wind_b <- filter(Hurricanes_2019, WMO_WIND >34)
unique_Hurricanes_2019_1 <- unique(select(Hurricanes_2019_wind_b, SID))
unique_Hurricanes_2019_1




```

b) The 2019 atlantic hurricane season had six named storms that achieved hurricane
status.

```{r}
# False, the 2019 Atlantic hurricane season had seven named storms that achieved hurricane status.
Hurricanes_2019_wind_b <- filter(Hurricanes_2019 , WMO_WIND >=64)
uniqueb <- unique(select(Hurricanes_2019_wind_b, NAME))
uniqueb

distinct(Hurricanes_2019, WMO_WIND >= 64)
```

c) The 2019 atlantic hurricane season had three named storms that intensified into major
hurricanes, all of which became Category 5 hurricanes.

```{r}
# False, the 2019 Altlantic hurricane season had three named storms that intensified into majoy hurricanes, only two of which became Category 5 hurricanes.
Hurricanes_c1 <- filter(Hurricanes_2019 , WMO_WIND >= 96)
Hurricanes_c2 <- filter(Hurricanes_2019 , WMO_WIND >= 137)

uniquec1 <- unique(select(Hurricanes_c1, NAME))
uniquec2 <- unique(select(Hurricanes_c2, NAME))

uniquec1
uniquec2

distinct(Hurricanes_2019, WMO_WIND >= 96)
distinct(Hurricanes_2019, WMO_WIND >= 137)
```

d) There was one storm in 2019 that formed outside the official hurricane season (recall
that the official season goes from June 1 to November 30).

```{r}
#Yes, there was one storm in 2019 that formed outside the official hurricane season, and the name of this storm is Andrea.
Hurricanes_2019$ISO_TIME = as.POSIXct(Hurricanes_2019$ISO_TIME)
Hurricanes_2019$MONTH <- lubridate::month(Hurricanes_2019$ISO_TIME)

Hurricanes_2019_d <- filter(Hurricanes_2019, SEASON == 2019 ,  !MONTH %in% 6:11)
uniqued <- unique(select(Hurricanes_2019_d, NAME))

uniqued

distinct(Hurricanes_2019,  !MONTH %in% 6:11)
```

e) Two storms became Category 5 hurricanes, at least one storm making landfall at
Category 5 intensity.

```{r}
#FALSE, it doesn't exist one storm makeing landfall at Categort 5 intensity.
distinct(Hurricanes_2019, WMO_WIND >137)
distinct(Hurricanes_2019,LANDFALL == '0'& WMO_WIND >= 137)

```

C.4) Animated Map
Make an animated map of storms in 2019, to display their paths (or trajectories). And don’t
forget to provide a sound description and interpretation for this visual display.
To do this, you will have to plot the locations of the storms with their longitude and latitude
on a map. Start by making a static (i.e. non-animated) map following one of the approaches
described in Prof. Sanchez’s book
http://www.gastonsanchez.com/intro2cwd/eda-maps.html
To learn how to animate static ggplots, take a look at the tutorial Getting Started with the
package "gganimate" by Thomas Lin Pederson and David Robison:
https://gganimate.com/articles/gganimate.html
You can see an example of various animated graphics in An Intro to Animating Charts with
"gganimate" by Joe Drigo Enriquez.
https://rpubs.com/jedoenriquez/animatingchartsintro
Look at example 2 Australia vs New Zealand: life expectancy and GDP per capita especially
the section titled Animate the scatterplot, in which Joe Drigo uses the time variable
year and the function transition_time() to make the year-based animated transitions.




```{r}
C4data <- filter(Hurricanes, SEASON == 2019&WMO_WIND >=34)
world_map <- map_data("world")
gg_world <- ggplot() + 
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               fill = "gray95", colour = "gray70", size = 0.5) +
  theme_bw()
world <- gg_world + 
  geom_point(data = C4data, 
             aes(x = LON, y = LAT, color = NAME, size = WMO_WIND),   alpha = 0.5) + 
   xlim(c(-110, 0)) + 
  ylim(c(0, 60)) 
 gif <- world + transition_time(ISO_TIME)+
 labs(title = '{frame_time}')
animate(gif,fps = 5)
```


